Untitled

### 2021-03-13 ms/manuscript.Rmd
Add image file for fig 1
Use rmarkdown parameters to print figures or not

---
title: ""
bibliography: 
  - references.bib
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 12pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-plant-research.csl"]
    includes:
      in_header: journal-of-plant-research.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
params:
  output_type: ms_for_word
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

<!-- to move to the next line without starting a new paragraph, 
add two spaces after last word, e.g., Atsushi Ebihara__ -->

@@

## Figure legends
<!-- JPR requirements: Figure captions begin with the term Fig. in bold type, followed by the figure number, also in boldtype. No punctuation is to be included after the number, nor is any punctuation to be placed at the end of the caption. -->

@@

```{r filmies-fig, fig.width = 6.85, results = "asis", purl = FALSE}
knitr::include_graphics(here::here("data/figure_1.png"))
```

**`r figure("habit")`**

```{r filmy-dt-plot, fig.width = 6.85, fig.height = 7.5, fig.cap = "", purl = FALSE}
make_dt_plot(dt_plot_data, "sporophyte", "a")
figname <- figure("dt") %>% str_remove_all("[:punct:]| ") %>% paste0("a.pdf")
ggsave(file = here::here("results/ms", figname), width = 6.85, height = 7.5)
```

**`r figure("dt")`**

```{r gameto-dt-plot, fig.width = 6.85, fig.height = 7.5, fig.cap = "", purl = FALSE}
make_dt_plot(dt_plot_data, "gametophyte", "b")
figname <- figure("dt") %>% str_remove_all("[:punct:]| ") %>% paste0("b.pdf")
ggsave(here::here("results/ms", figname), width = 6.85, height = 6.5, device = "pdf")
```

**`r figure("dt")`** (continued)

```{r combined-plot, fig.width = 6.85, fig.height = 5, fig.cap = "", purl = FALSE}
# Copy data so they can be manipulated for this plot
phy <- filmy_phy
traits <- combined_species_means
habit <- filmy_habit

@@

# Combine plots
a + b + c + d + plot_layout(nrow = 1, guides = "collect") &
  theme(
    legend.position = "bottom",
    # Adjust invididual margins to remove whitespace between subplots
    plot.margin = margin(t = 0.1, r = 0, b = 0.1, l = 0.04, unit = "in"),
    # Wrap legend parts into multiple lines
    legend.box = "vertical", 
    legend.margin = margin())

figname <- figure("combined") %>% str_remove_all("[:punct:]| ") %>% paste0(".pdf")
ggsave(here::here("results/ms", figname), width = 6.85, height = 5)
```

**`r figure("combined")`**

```{r corr-plot, fig.width = 6.85, fig.height = 5, fig.cap = "", purl = FALSE}
# Combine recovery, VPD, and growth habit into a single dataframe (wide format)
recovery_mean_data <- select(combined_species_means, species, generation, recovery_mean) %>%
  pivot_wider(values_from = recovery_mean, names_from = generation) %>%
  rename_with(~glue("recovery_{.}_mean"), .cols = -species)

@@

a + b + c + 
  guide_area() + 
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "a")  &
  theme(plot.tag = element_text(face = 'bold'))

figname <- figure("corr") %>% str_remove_all("[:punct:]| ") %>% paste0(".pdf")
ggsave(here::here("results/ms", figname), width = 6.85, height = 5)
```

**`r figure("corr")`**

>>>>

---
title: ""
bibliography: 
  - references.bib
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 12pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes # for converting tex to doc
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-plant-research.csl"]
    includes:
      in_header: journal-of-plant-research.sty
# Prevent figures from moving around, suppress automatic "Figure #:" in captions
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
  \renewcommand{\caption}{}
params:
  output_type: "ms"
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

<!-- to move to the next line without starting a new paragraph, 
add two spaces after last word, e.g., Joel Nita__ -->

@@

## Figure legends

<!-- JPR requirements: Figure captions begin with the term Fig. in bold type, followed by the figure number, also in boldtype. No punctuation is to be included after the number, nor is any punctuation to be placed at the end of the caption. -->

@@

<!-- From here, use params$output_type to output plots directly for preprint PDF, or save to file for journal submission -->

```{r filmies-print, fig.width = 6.85, results = "asis", fig.cap = figure("habit"), eval = params$output_type == "preprint", purl = FALSE}
# Print plot if knitting MS to preprint
knitr::include_graphics(here::here("images/figure_1.png"))
```

```{r filmy-dt-plot-make, purl = FALSE}
# Make plot
filmy_dt_plot <- make_dt_plot(dt_plot_data, "sporophyte", "a")
```

```{r filmy-dt-plot-save, eval = params$output_type == "ms", purl = FALSE}
# Save plot to file if knitting MS for submission
filmy_dt_plot_name <- figure("dt") %>% str_remove_all("[:punct:]| ") %>% paste0("a.pdf")
ggsave(plot = filmy_dt_plot, file = here::here("results/ms", filmy_dt_plot_name), width = 6.85, height = 7.5)
```

```{r filmy-dt-plot-print, fig.width = 6.85, fig.height = 7.5, fig.cap = figure("dt"), eval = params$output_type == "preprint", purl = FALSE}
# Print plot if knitting MS to preprint
filmy_dt_plot
```

```{r gameto-dt-plot-make, purl = FALSE}
# Make plot
gameto_dt_plot <- make_dt_plot(dt_plot_data, "gametophyte", "b")
```

```{r gameto-dt-plot-save, eval = params$output_type == "ms", purl = FALSE}
# Save plot to file if knitting MS for submission
gameto_dt_plot_name <- figure("dt") %>% str_remove_all("[:punct:]| ") %>% paste0("b.pdf")
ggsave(plot = gameto_dt_plot, file = here::here("results/ms", gameto_dt_plot_name), width = 6.85, height = 6.5, device = "pdf")
```

```{r gameo-dt-plot-print, fig.width = 6.85, fig.height = 7.5, fig.cap = paste(figure("dt"), "(continued)"), eval = params$output_type == "preprint", purl = FALSE}
# Print plot if knitting MS to preprint
gameto_dt_plot
```

```{r combined-plot-make, purl = FALSE}
# Make plot

# Copy data so they can be manipulated for this plot
phy <- filmy_phy
traits <- combined_species_means
habit <- filmy_habit

@@

# Make combined plot
combined_plot <- a + b + c + d + plot_layout(nrow = 1, guides = "collect") &
  theme(
    legend.position = "bottom",
    # Adjust invididual margins to remove whitespace between subplots
    plot.margin = margin(t = 0.1, r = 0, b = 0.1, l = 0.04, unit = "in"),
    # Wrap legend parts into multiple lines
    legend.box = "vertical", 
    legend.margin = margin())
```

```{r combined-plot-save, eval = params$output_type == "ms", purl = FALSE}
# Save plot to file if knitting MS for submission
combined_plot_name <- figure("combined") %>% str_remove_all("[:punct:]| ") %>% paste0(".pdf")
ggsave(plot = combined_plot, file = here::here("results/ms", combined_plot_name), width = 6.85, height = 5)
```

```{r combined-plot-print, fig.width = 6.85, fig.height = 5, fig.cap = figure("combined"), eval = params$output_type == "preprint", purl = FALSE}
# Print plot if knitting MS to preprint
combined_plot
```

```{r corr-plot-make, fig.width = 6.85, fig.height = 5, fig.cap = "", purl = FALSE}
# Make plot

# Combine recovery, VPD, and growth habit into a single dataframe (wide format)
recovery_mean_data <- select(combined_species_means, species, generation, recovery_mean) %>%
  pivot_wider(values_from = recovery_mean, names_from = generation) %>%
  rename_with(~glue("recovery_{.}_mean"), .cols = -species)

@@

corr_plot <- a + b + c + 
  guide_area() + 
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "a")  &
  theme(plot.tag = element_text(face = 'bold'))
```

```{r corr-plot-save, eval = params$output_type == "ms", purl = FALSE}
# Save plot to file if knitting MS for submission
corr_plot_name <- figure("corr") %>% str_remove_all("[:punct:]| ") %>% paste0(".pdf")
ggsave(plot = corr_plot, file = here::here("results/ms", corr_plot_name), width = 6.85, height = 5)
```

```{r corr-plot-print, fig.width = 6.85, fig.height = 5, fig.cap = figure("corr"), eval = params$output_type == "preprint", purl = FALSE}
# Print plot if knitting MS to preprint
corr_plot
```
